Critical Temperature of YBCO and BSCCO Superconductors

### 2014-12-04 Draft.tex
comments on procedure.
Generally OK. Needs more detail (as does everything). Description of
why voltage drop occurs across a thermocouple junction is physically
wrong and needs revision.

\section{Procedure}
The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. Each superconductor  is contained in a brass casing with three pairs of leads. 
One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
The thermocouple has a resistance that varies with temperature, so we can determine the  temperature of superconductor by measuring the voltage across the thermocouple.

We used different methods to measure the critical temperature of the two superconductors.
For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. 
The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple, $V_{T}$ were measured with two nanovoltmeters. We placed the superconductor inside a styrofoam cup filled with sand. 
The sand reduces the rate at which the superconductor heats up, which allows us to gather more data points. 
We cooled the YBCO sample by pouring liquid nitrogen into the styrofoam cup. We waited for the superconductor to settle to a minimum temperature. Then we recorded $V_{\textrm{YBCO}}$ and $V_{T}$ as it warmed up to above its critical temperature.

We used a two-phase lock-in amplifier for the BSCCO experiment. In an AC circuit, the measurement of resistance includes contributions from capacitors and inductors. 
Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used. 
The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions because the resistance will be in phase with the signal, while the contributions of capacitors and inductors will be out of phase. 
Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can get approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source of 1 V.

>>>>

\section{Procedure}
The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. Each superconductor  is contained in a brass casing with three pairs of leads. 
One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
\textcolor{red}{The thermocouple has a resistance that varies with temperature}, so we can determine the  temperature of superconductor by measuring the voltage across the thermocouple. \textcolor{blue}{NOT a resistance measurement! If it were a resistance, it would require the application of a current to generate a voltage drop across it. See http://en.wikipedia.org/wiki/Thermocouple }

We used different methods to measure the critical temperature of the two superconductors.
For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. 
The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple \textcolor{magenta}{junction}, $V_{T}$ were measured with two nanovoltmeters. \textcolor{blue}{you should explain the point of reversing the current and how this helps more accurately determine the true }$\Delta V$ \textcolor{blue}{ across the sample. You should also explain how you go from voltage drop to resistance, even though it is a simple calculation, or that the instrument does that for you. Finally, didn't you do some measurements at other values of current?}

We placed the superconductor inside a styrofoam cup filled with sand. 
The sand reduces the rate at which the superconductor heats up, which allows us to gather more data points. 
We cooled the YBCO sample by pouring liquid nitrogen into the styrofoam cup. We waited for the superconductor to settle to a minimum temperature. Then we recorded $V_{\textrm{YBCO}}$ and $V_{T}$ as it warmed up to above its critical temperature.

We used a two-phase lock-in amplifier for the BSCCO experiment. An AC circuit \textcolor{magenta}{set up for the} measurement of resistance \textcolor{magenta}{is also susceptible to (or includes) } contributions from \textcolor{magenta}{parasitic capacitances and inductances between wires and to ground (or capacitors and inductors)}. 
Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used \textcolor{magenta}{and construction of the circuit}. 
The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions because the resistance will be in phase with the \textcolor{red}{signal}, while the contributions of capacitors and inductors will be out of phase. \textcolor{blue}{the in phase component IS your signal. I think you mean that the voltage drop across the sample due to its resistance will be in phase with the applied ac voltage from the oscillator, but of course you can say this more succinctly}. 
Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate \textcolor{magenta}{an AC current with an RMS amplitude of approximately} $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source \textcolor{magenta}{with an RMS amplitude} of 1 V.
